%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
% 
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
% 
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
% 
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
% 
% Important notes:
% This template needs to be compiled with XeLaTeX.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

% ----------------------------------------------------------------------------------------
%	TITLE SECTION
% ----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Doug}{Raffle}{ % Your name
  \bf{\href{mailto:raffled@gmail.com}{raffled@gmail.com}} $\;$|$\;$
  \urlstyle{same}\url{www.dougraffle.com} $\;$|$\;$
  \bf{724.518.7446}
}

% ----------------------------------------------------------------------------------------
%	LEFT COLUMN
% ----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth} % The left column takes up 30% of the text width of the page

  % ------------------------------------------------
  % Education
  % ------------------------------------------------

  \section{Education} 
  \subsection{West Virginia University}
  \descript{MS in Statistics\\}
  \location{Aug. 2015 | Morgantown, WV\\}
  \sectionspace % Some whitespace after the section

  % ------------------------------------------------

  \subsection{California University}
  \subsection{of Pennsylvania}
  \descript{BS in Computer Science\\}
  \descript{Minor in Mathematics\\}
  \location{May 2013 | California, PA\\}

    \vspace{30pt}

  % ------------------------------------------------
  % Links
  % ------------------------------------------------

  \section{Links} 
  {\bf Website://}\\ \href{http://www.dougraffle.com/}{dougraffle.com/}\\
  {\bf Github://}\\ \href{http://github.com/raffled/}{github.com/raffled/}\\
  {\bf LinkedIn://}\\ \href{https://www.linkedin.com/in/raffled}{linkedin.com/in/raffled} \\
  
  \vspace{30pt}
  % ------------------------------------------------
  % Skills
  % ------------------------------------------------
  
  \section{Skills}
  \subsection{Leading}
  End-to-End Data Science Lifecycle\\
  Cloud-native Data Science\\
  Generative \& Agentic AI\\
  Responsible AI\\
  Innovation \& Incubation Projects\\
  Agile Project Management\\
  Data Science Best Practices \& Community Development\\
  
  \vspace{10pt}
  
  \subsection{Contributing}
  Statistical Modeling\\
  Multivariate Statistics\\
  Data Mining \& Machine Learning\\
  Model \& Process Automation\\
  Software \& Data Engineering\\
  Data Visualization\\
  Teaching \& Public Speaking\\

  \sectionspace % Some whitespace after the section
  \vspace{3pt}
  % ------------------------------------------------
  % Technologies
  % ------------------------------------------------

  \sectionspace % Some whitespace after the section
  \vspace{3pt}
  % ------------------------------------------------
  % Programming
  % ------------------------------------------------
  % \subsection{Languages}
  % {\bf Strong\\}
  % R\\
  % SQL\\
  % \vspace{4pt}
  % {\bf{Familiar\\}}
  % Python\\
  % Java\\
  % \vspace{4pt}

  % ----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
% 
% ----------------------------------------------------------------------------------------
%	RIGHT COLUMN
% ----------------------------------------------------------------------------------------
% 
\begin{minipage}[t]{0.68\textwidth}
  % ------------------------------------------------
  % Objective
  % ------------------------------------------------
  % \section{Summary}
  % I am a data scientist and statistician with a strong background in
  % both software development and statistical analysis.  My experience in
  % teaching and research has allowed me the opportunity to not only learn
  % and implement a variety of statistical and machine learning models,
  % but also hone my presentation skills and work closely with experts in a
  % variety of fields.  My goal is to find a challenging
  % position where I can solve novel problems and make data-driven
  % policy recommendations.

  % ------------------------------------------------
  % Experience
  % ------------------------------------------------

  \section{Experience}
  \runsubsection{The Hartford}\hfill\location{Hartford, CT\\}
  \sectionspace
  
  \subsection{\emph{Claims \& Operations Data Science}}
  
  \descript{AVP Data Science | Emerging Sciences}\hfill
  \location{Jan. '25 - Present\\}
  \descript{Dir. Data Science | Emerging Sciences}\hfill
  \location{Dec. '23 - Jan '25\\}
  \vspace{\topsep}
  \begin{tightitemize}
    \item Lead Data Science and AI team building and continuing to expand the first fully automated, large scale GenAI summarization \&
      information extraction solution at The Hartford for over 2,000 daily active users. 
      Now fully released, this capability is expected to provide more than \$5mm in annual expense benefit 
      by summarizing medical Records related to WC and EB claims.
    \item Proved viability and established benefit estimates of our summarization engine quickly by prototyping and 
      deployed non-integrated Test \& Learn less than 8 weeks and full production pilot, including a rebuild upstream dependencies for summarization, 
      in less than 12 weeks.
    \item Tightly Coordinated with more than a dozen Data Science, Technology, Strategy, and Claims teams
      to plan, validate, and execute production roll-out of GenAI work within the Claims space.
    \item Partner closely with centralized Data Science \& AI Acceleration \& Platform teams to prototype and
    identify MVP requirements for emergent AI solutions, including workflow and autonomous agentic solutions.
    \item Proposed and established the first fully-federated Line of Business GenAI team with The Hartford.
    \item Continue to participate in the creation of long term capability roadmaps for GenAI 
      use-cases with Claims \& Operations, identifying both opportunities for production 
      work and an experimental/POC backlog.
    \item Participated in vendor engagements for POCs and demos in addition to coordinating
      training \& enablement with external partners like AWS and Anthropic.
  \end{tightitemize}
  \sectionspace
  
  \descript{Dir. Data Science | WC \& EB Claims}\hfill
  \location{July '22 - Dec '23\\}
  %\vspace{\topsep}
  \begin{tightitemize}
    \item Built and maintained ML \& AI models in a robust portfolio of solutions designed to triage, automate, or 
    identify claims for specialist intervention (e.g., fraud, clinical, financial risk).
    \item Oversaw five production releases of model-driven solutions in both batch and real time
      delivery frameworks with my first year on the team.
    \item Matured monitoring, bias detection \& mitigation, and other model lifecycle management practices across Claims Data Science.
    \item Took a leadership role in a complete overhaul of Data Science job families
      across the enterprise.
  \end{tightitemize}
  \sectionspace
  
  \runsubsection{Actuarial Technology \& Innovation (AcTech)\\}
  \descript{Dir. Data Science | AcTech Pricing \& Consulting}\hfill
  \location{Sept. '21 - July '22\\}
  %\vspace{\topsep}
  \begin{tightitemize}
  \item Owned the suite of Commercial Lines Risk Score \& Pricing models
    and the monitoring, modeling, and deployment infrastructure needed
    to maintain them. The total portfolio allocated over \$3bn in in-force
    premium across Auto, Property, General Liability, and
    Workers Compensation for both Middle \& Large and Small Commercial
    policies.
  \item Managed and mentored data scientists, engineers, and actuaries assigned to both
   Consulting and Pricing work streams.

  \end{tightitemize}
  \sectionspace

  

  

  

  % \location{See LinkedIn for full work history.}

\end{minipage} % The end of the right column
\newpage

% ------------------------------------------------------------------
% Page 2
% ------------------------------------------------------------------

% ----------------------------------------------------------------------------------------
%	TITLE SECTION
% ----------------------------------------------------------------------------------------

\namesection{Doug}{Raffle}{ % Your name
  \bf{\href{mailto:raffled@gmail.com}{raffled@gmail.com}} $\;$|$\;$
  \urlstyle{same}\url{www.dougraffle.com} $\;$|$\;$
  \bf{724.518.7446}
}


% \begin{minipage}[t]{0.3\textwidth} % The left column takes up 33% of
%   % the text width of the page
% \end{minipage} % The end of the left column

% \hfill
% \hfill

\begin{minipage}[t]{0.9\textwidth}

  \section{Experience (Cont'd)}
  
  \descript{Dir. Data Science | AcTech Consulting}\hfill
  \location{Mar. '21 - Sept. '21\\}
  \vspace{\topsep}
  \begin{tightitemize}
  \item  Expanded the AcTech Consulting team from just myself and one
    associate data scientist to a diverse team of five data scientists
    and data engineers in a year. 
  \item Broadened the scope of the Consulting portfolio from modeling focused projects to
    also include data engineering efforts (e.g., building new data
    pipelines, process re-engineering, building interactive
    analytical/reporting apps).
  \item Consulted with Actuarial leadership on the adoption of emerging
    technologies/platforms and incorporating statistical modeling,
    machine learning, and modern data technologies into their business
    processes.
  \end{tightitemize}
  \sectionspace
  
  \descript{Sr. Data Scientist | AcTech Training}\hfill\location{Oct. '18 - Mar. '21\\}
  % \vspace{\topsep}
  \begin{tightitemize}
  \item   Founded the AcTech Consulting team, which works across the Actuarial
    organization and helped to accelerate modeling and automation
    focused projects across all lines of business. 
  \item Fit a variety of statistical models and machine learning
    algorithms to modernize or enhance existing Actuarial processes
    (e.g., stochastic reserve modeling, modeled rate indications, claim-level
    loss development) and worked with Actuarial partners to integrate
    these insights into their workflows.
  \item Designed curriculum for and conducted classroom-based training in an
    intensive 8-week program for actuaries. This evolving course teaches modern data
    science techniques and data technologies and includes a hands-on
    capstone project.
  \end{tightitemize}
  \sectionspace
  
  \runsubsection{Small Commercial Data Science\\}
  \descript{Data Scientist | Underwriting Triage}\hfill
  \location{Feb. '17 - Oct. '18\\}
  % \vspace{\topsep}
  \begin{tightitemize}  
  \item Designed and implemente model
    scoring engine to serve live predictions from a suite of machine
    learning algorithms (via a RESTful web service) as part of a Chairman's Award-winning
    initiative to streamline the quoting process for customers.
  \item Fit machine learning algorithms to predict customer characteristics, triage new and
  renewal business, and generally assist in the underwriting process using
    large first and third party data sources.
  \end{tightitemize}
  \sectionspace
  
  \runsubsection{Mylan Labs (Viatris)}\hfill\location{Morgantown, WV\\}
  \descript{Specialist | Commercial Analytics}\hfill\location{Sept. '15 - Jan. '17\\}
  \begin{tightitemize}
  \item Acted as an internal consultant, using statistical models and machine
    learning algorithms to 
    analyze Mylan's products, customers, and competitors using R and
    other statistical packages.
  \item Designed presentations summarizing Mylan's major product markets,
    including product and competitor performance, for senior leadership.
  \item Modernized reporting and presentation workflows using Tableau and
    Shiny to create streamlined, interactive dashboards.
  \end{tightitemize}
  \sectionspace % Some whitespace after the section

  % ------------------------------------------------

  \runsubsection{California University of Pennsylvania}\hfill\location{California, PA\\}
  \descript{Lecturer | Business Statistics}\hfill
  \location{Jan. '16 - Dec. '16\\}
  \begin{tightitemize}
  \item Used real world experience as a data scientist to introduce
    students from the business college to the concepts they'll need to
    work in a modern, data-driven  business environment.
  \end{tightitemize}
  \sectionspace % Some whitespace after the section

  % ------------------------------------------------

  % \runsubsection{West Virginia University}\hfill\location{Morgantown, WV\\}
  % \descript{Graduate Teaching Assistant}\hfill\location{Aug. '13 - Aug. '15\\}
  % % \vspace{\topsep} % Hacky fix for awkward extra vertical space
  % \begin{tightitemize}
  % \item Taught and designed coursework for laboratory and
  %   lecture sections of undergraduate Statistics courses.
  % \item Worked with the director of the Master's of Data Science program
  %   to design online coursework.
  % \end{tightitemize}

  \sectionspace
  
  \section{Awards \& Honors}
  \descript{Tech \& Ops Visionary Award: Medical Records Summarization}\hfill\location{2024}\\
  \descript{Chairman's Award: Small Business Owner Score}\hfill\location{2018}\\
  \descript{WVU Outstanding Graduate Teaching Assistant}\hfill\location{2014}\\
  
  \sectionspace
  
  \section{Volunteer/Service Experience}
  \descript{RiderCoach, Motorcycle Safety Foundation}\hfill\location{2023+}\\
  \descript{Mentor, Correlation One / Data Science for All (DS4A)}\hfill\location{2021}\\
  \descript{Math Buddy, HIG Math \& Reading Buddies}\hfill\location{2018-2019}\\
  
  
  
  % 
  % \runsubsection{HIG Math \& Reading Buddies}\hfill\location{Hartford, CT\\}
  % \descript{Math Buddy}\hfill
  % \location{Sept. '18 - May '19\\}
  % \begin{tightitemize}
  % \item  Worked with 4th grade math students in a downtown Hartford
  %   school to help teach them mathematics skills and introduce them to
  %   math-focused careers. 
  % \end{tightitemize}

\end{minipage}
\end{document}
