%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

% \lastupdated % Print the Last Updated text at the top right

\namesection{Doug}{Raffle}{ % Your name
  \bf{\href{mailto:raffled@gmail.com}{raffled@gmail.com}} $\;$|$\;$
  \urlstyle{same}\url{www.dougraffle.com}
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.35\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 
\subsection{West Virginia University}
\descript{MS in Statistics}
\location{Aug. 2015 | Morgantown, WV}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{California University}
\subsection{of Pennsylvania}
\descript{BS in Computer Science}
\descript{Minor in Mathematics}
\location{May 2013 | California, PA}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 
{\bf Portfolio://}\\ \href{http://www.dougraffle.com/portfolio.html}{dougraffle.com/portfolio.html}\\
{\bf Github://}\\ \href{http://github.com/raffled/}{github.com/raffled/}\\
{\bf LinkedIn://}\\ \href{https://www.linkedin.com/in/raffled}{linkedin.com/in/raffled} \\
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}
\subsection{Major Skill Sets}
Data Technologies\\
Statistical Modeling\\
Multivariate Statistics\\
Data Mining/Machine Learning\\
Business Intelligence\\
Software Development\\
Data Visualization\\
Text Mining\\
Technical Writing/Presentation

\sectionspace % Some whitespace after the section
\vspace{5pt}
%------------------------------------------------
% Technologies
%------------------------------------------------
\subsection{Technologies/Platforms}
Microsoft Office\\
JMP\\
Hadoop/MapReduce\\
Linux/Unix\\
Tableau\\
RStudio\\
Shiny

\sectionspace % Some whitespace after the section
\vspace{5pt}
%------------------------------------------------
% Programming
%------------------------------------------------
\subsection{Programming Languages}
\location{\textbf{Strong}}
R\\
HTML/XML\\
\LaTeX\\
Markdown/R Markdown\\
\vspace{5pt}
\location{\textbf{Familiar}}
JavaScript\\
LISP\\
Python\\
SQL\\


%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.63\textwidth} % The right column takes up 63% of
                                % the text width of the page
%------------------------------------------------
% Objective
%------------------------------------------------
% \section{Summary}
% I am a data scientist and statistician with a strong background in
% both software development and statistical analysis.  My experience in
% teaching and research has allowed me the opportunity to not only learn
% and implement a variety of statistical and machine learning models,
% but also hone my presentation skills and work closely with experts in a
% variety of fields.  My goal is to find a challenging
% position where I can solve novel problems and make data-driven
% policy recommendations.

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}
\runsubsection{Mylan Labs}
\descript{| Specialist, Commercial Analytics}
\location{Sept. 2015 - Jan. 2017 | Morgantown, WV}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Acted as an internal consultant, using statistical models and machine
  learning algorithms to 
  analyze Mylan's products, customers, and competitors using R and
  other statistical packages.
\item Designed presentations summarizing Mylan's major product markets,
  including product and competitor performance, for senior leadership.
\item Modernized reporting and presentation workflows using Tableau and
  Shiny to create streamlined, interactive dashboards.
\end{tightitemize}
\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{California University of Pennsylvania}
\descript{| Lecturer}
\location{Jan. 2016 - Dec. 2016 | California, PA}
\begin{tightitemize}
\item Used real world experience as a data scientist to introduce
  students from the business college to the concepts they'll need to
  work in a modern, data-driven  business environment.
\end{tightitemize}
\sectionspace % Some whitespace after the section

%------------------------------------------------


\runsubsection{West Virginia University}
\descript{| Graduate Teaching Assistant}
\location{Aug. 2013 – Aug. 2015 | Department of Statistics | Morgantown, WV}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Taught and designed coursework for laboratory and
  lecture sections of undergraduate Statistics courses.
\item Worked with the director of the Master's of Data Science program
  to design online coursework.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{West Virginia University}
\descript{| Graduate Research Assistant}
\location{May 2014 – Sept. 2014 | West Virginia Dialect Project |
  Morgantown, WV}
\begin{tightitemize}
\item Consulted with linguists on evaluating and creating analysis workflows.
\item Built and evaluated Linear and Generalized Linear Mixed Effects
  models used in the investigation of sociolinguistic trends.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{California University of Pennsylvania}
\descript{Undergraduate Research Assistant}
\location{Sept. 2010 – May 2013 | The Lexomics Project |
  California, PA \& Norton, MA}
\begin{tightitemize}
\item Used statistical models and machine learning algorithms to analyze
  works of literature for stylistic variation and analyze the features
  that are most indicative of clustering behavior.
\item Presented at several conferences and co-authored a paper
  explaining our methodology and results.
\end{tightitemize}

\sectionspace % Some whitespace after the section
\vspace{-3pt}
\section{Consulting}
\runsubsection{Sellitti, Nogay \& McCune, PLLC}\\
\location{June 2015 | Weirton, WV}
\begin{tightitemize}
\item Analyzed a survey conducted by the court to determine if
  local news stories had biased potential jurors against the defendant in a
  murder case.
\item Wrote a report used as evidence in a hearing to determine if
  outside jurors needed to be used.
\end{tightitemize}

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Awards
%------------------------------------------------
\vspace{-7pt}
\section{Awards and Grants} 

\begin{tabular}{rl}
2014 & Outstanding Graduate Teaching Assistant Award (WVU)\\
2012 & Second Place - Student Scholarship and Creativity Day (CalU)\\
2011 & Jesse B. Guttman Student Research Grant\\
\end{tabular}

\sectionspace % Some whitespace after the section



%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column
\end{document}
