%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
%\usepackage[margin=2.5cm]{geometry}
\usepackage{longtable}
\usepackage{array, xcolor}
\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
\newcolumntype{R}{p{0.8\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Doug}{Raffle}{ % Your name
  \bf{\href{mailto:douglas.raffle@mylan.com}{douglas.raffle@mylan.com}} $\;$|$\;$
  \urlstyle{same}\url{http://stat.wvu.edu/~draffle/} $\;$|$\;$
  \bf{724.518.7446}
}


\section{Education}
\begin{flushleft}
\runsubsection{MS in Statistics} \\
\location{West Virginia University, 2015}
\vspace{8pt}
\runsubsection{BS in Computer Science} \\
\descript{Minor in Mathematics}
\location{California University of Pennsylvania, 2013}
\end{flushleft}

\sectionspace

\section{Teaching Experience}
\begin{flushleft}
\runsubsection{Lecture Instructor}
\descript{|\hspace{4pt} 2015}
\location{West Virginia University, Department of Statistics}
\vspace{-8pt}
\begin{longtable}{L R}
Course: & Understanding Statistics\\
\end{longtable}

\runsubsection{Lab Instructor}
\descript{|\hspace{4pt} 2013 {\textendash} 2015}
\location{West Virginia University, Department of Statistics}
\vspace{-8pt}
\begin{longtable}{L R}
Courses: & Elementary Statistical Inference, Understanding Statistics\\
\end{longtable}

\end{flushleft}

\sectionspace

\section{Industry Experience}
\runsubsection{Specialist, Commercial Insights}
\descript{|\hspace{4pt} 2015 {\textendash} Present}
\location{Mylan Pharmaceuticals | Morgantown, WV}
As a member of the Commercial Insights team, I apply statistical methods in the business setting by:
\begin{tightitemize}
\item Using statistical models and machine learning algorithms to
  perform market intelligence analysis and performance analytics for
  Mylan's products, business units, customers, and competitors.
\item Consulting directly with other departments to provide ad-hoc
  statistical analyses to answer specific business questions. 
\end{tightitemize}

\sectionspace

\section{Other Academic Experience}
\runsubsection{Graduate Teaching Assistant}
\descript{|\hspace{4pt} 2013 {\textendash} 2015}
\location{West Virginia University, Department of Statistics}
In addition to teaching responsibilities, my teaching assistantship at 
WVU also included:
\begin{tightitemize}
\item Designing Quality Matters compliant online coursework for WVU's Masters of Data Science program
\item Providing one-on-one tutoring for all of the Statistic Department's undergraduate courses
\item Designing and modifying homework, quiz, and test questions in Pearson's MyStatLab to fit with other professors' curricula
\end{tightitemize}

\vspace{8pt}

\runsubsection{Graduate Research Assistant}
\descript{|\hspace{4pt} 2014}
\location{West Virginia University, Department of Statistics}
I consulted with the West Virginia Dialect project, performing statistical analysis and training
linguists and undergraduate researchers in statistical methods and data visualization

\vspace{8pt}

\newpage

\section*{Publications}
Downey, S., Drout, M.D.C., Kerekes, V., and Raffle, D. (2014). “Lexomic Analysis of Medieval Latin Texts,” {\em Journal of Medieval Latin} 24, 225-74.

\sectionspace

\section*{Conference Presentations}
\begin{longtable}{L!{\VRule}R}
2015 & ``An Introduction to Realtime Computation with RStorm and twitteR''\\
& Douglas Raffle \\
&  Presentated at: The 45th Symposium On The Interface of
Computing Science And Statistics. June 13, 2015.\vspace{5pt}\\

& ``twitterRStorm: Prototyping a Streaming Framework for Analyzing Tweets with Storm''\\
& Douglas Raffle \\
& Tutorial Given at: The 45th Symposium On The Interface of
Computing Science And Statistics. June 13, 2015.\vspace{5pt}\\

2013 & ``Using a Discussion-Based Approach in an Upper Level Statistics Course''\\ 
& Douglas Raffle, Melissa M. Sovak \\
& Peer-Reviewed Presentation at: The United States Conference on
Teaching Statistics.  May 17, 2013.\vspace{5pt}\\   

2012 & ``Computational Analysis of Medieval Latin:
Using Computational Linguistics to Identify Borrowed and Interpolated Material from Medieval History Texts''\\
& Sarah Downey, Douglas Raffle\\
 &Presented at: The California University of Pennsylvania Faculty and
 Professional Development Committee Lunch Series. November 17,
 2012. \vspace{5pt}\\  

& ``LightSIDE and Lexomics: Comparing the Results of Supervised Machine-Learning Classification
Algorithms to Agglomerative Hierarchical Cluster Analysis in the Identification of Borrowed or Interpolated
Material in Medieval Latin Manuscripts''\\
& Douglas Raffle \\
& Presented at: California University of Pennsylvania Student Scholarship and Creativity Day. April 24, 2012.\vspace{5pt}\\

& ``Latin Lexomics 1: Research Methods''\\
& Douglas Raffle\\
& Paper presented at: The English Association of Pennsylvania State
Universities Conference. April 7, 2012. \vspace{5pt}\\

2011 & ``Computational Analysis of Medieval Latin''\\
& Douglas Raffle \\
 &Presented at: California University of Pennsylvania Student
 Scholarship and Creativity Day. December 1, 2011. \vspace{5pt}\\

&  ``Latin Lexomics: Using Computational Linguistics to
  Identify Borrowed and Interpolated Material from Medieval History
  Texts''\\ 
&Veronica Kerekes, Douglas Raffle, Joshua Solomon, Richard
Williams\\
& Presented at: California University of Pennsylvania Academic
Excellence Days. April 20, 2011. \vspace{5pt}\\


& ``Latin Lexomics: Using Computational Linguistics to
  Identify Borrowed and Interpolated Material from Medieval History
  Texts''\\ 
&Veronica Kerekes, Douglas Raffle, Joshua Solomon, Richard
Williams\\
&Presented at: The 2nd Annual
Intersections Undergraduate Research Conference. April 15,
2011. \vspace{5pt}\\  
\end{longtable}

\sectionspace

\section{Awards and Grants}
\begin{longtable}{r| R}
2014 & WVU Eberly College of Arts and Sciences' Outstanding Graduate
       Teaching Assistant Award, Department of Statistics\vspace{5pt}\\
2012 & Second Place - California University of
       Pennsylvania's Student Scholarship and Creativity Day\vspace{5pt}\\
2011 & Jesse B. Guttman Student Research Grant\vspace{5pt}\\
     & Third Place - California University of Pennsylvania's
       Student Scholarship and Creativity Day\\
\end{longtable}

\section{Links}
{\bf Portfolio://} \href{http://stat.wvu.edu/~draffle/portfolio.html}{stat.wvu.edu/$\sim$draffle/portfolio.html}\\
{\bf Github://} \href{http://github.com/raffled/}{github.com/raffled/}\\
{\bf LinkedIn://} \href{https://www.linkedin.com/in/raffled}{linkedin.com/in/raffled} \\

\sectionspace

\section{References}
\runsubsection{Michael Mays}\\
Chair\\
Department of Statistics\\
West Virginia University\\
Email: \href{mailto:mmays@mail.wvu.edu}{mmays@mail.wvu.edu}\\
Phone: 304.293.9791\\

\vspace{10pt}

\runsubsection{E. James Harner}\\
Professor\\
Department of Statistics\\
West Virginia University\\
Email: \href{mailto:jharner@stat.wvu.edu}{jharner@stat.wvu.edu}\\
Phone: 304.293.9279\\

\vspace{10pt}

\runsubsection{Huey Miin Lee}\\
Teaching Associate Professor\\
Graduate Teaching Assistants Coordinator\\
Department of Statistics\\
West Virginia University\\
Email: \href{mailto:huey.lee@mail.wvu.edu}{huey.lee@mail.wvu.edu}\\
Phone: 304.293.3607 \\

\vspace{10pt}

\runsubsection{Sarah Downey}\\
Associate Professor\\
Department of English\\
California University of Pennsylvania\\
Email: \href{mailto:downey@calu.edu}{downey@calu.edu}\\
Phone: 724.938.4719

\end{document}
